Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-15 trunk/lids/twittersearchwrap/paper/paper.tex

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l|l}
Hashtag & Definition on tagdef.com & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
\#tilltheworldends & - & false & Britney Spears & .9583 \\
& & &  iTunes & .6875 \\
& & &  itunes & .625 \\ 
\hline
\#nowplaying & What people on Twitter & false & iTunes & .5208 \\
             & are currently listening & & Michael Jackson & .333 \\
             & to. & & Lady Gaga & .333 \\
\hline
\#nowplaying & same & true & YouTube & .8235 \\
             &  &  & Hip Hop Music & .6471 \\
             &  &  & The Notorious B.I.G. & .5883 \\
\hline
\#np         & Now playing = \#NP & false & Chris Brown\_(entertainer) & .5 \\
& & & Usher & .3125 \\
& & & Lil Wayne & .2917 \\
\hline
\#np & same & true & Chris Brown\_(entertainer) & .5 \\
& & & YouTube & .375 \\
& & & Ne-Yo & .315 \\
\hline
\#thataintwinning & -& false & Mozilla Firefox & .2291 \\
& & & Twitter & .2291 \\
& & & twitter & .1667 \\
\hline
\#thataintwinning & - & true & twitter & .5208 \\
& & & Twitter & .5 \\
& & & Two and a half men & .125 \\
\hline
\#blackpeoplemovies & - & false & Devil & .4791 \\
& & & Tyler Perry & .2708 \\
& & & Harry Potter & .2292 \\
\hline
\#blackpeoplemovies & - & true & Amazon.com & 1 \\
& & & YouTube & 1 \\
& & & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

@@

We have presented an approach for annotating Twitter hashtags with Wikipedia entities.
We have described an implementation of two variants of the method and evaluated the approach.

Our evaluation has shown that a direct mapping of hashtags to a single DBpedia concept is not always possible.
One reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
Another reason is the use of hashtags for different entities.
For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
The tag $\#ka$ is however also used to denote the car type Ford Ka.
Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
An approach which aims at finding relevant entities for a given search will have to be able to disambiguate homonym hashtags.
%deal with these problems.

>>>>

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l|l}
Hashtag & Definition on tagdef.com & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
\#tilltheworldends & - & false & Britney Spears & .9583 \\
& & &  iTunes & .6875 \\
& & &  itunes & .625 \\ 
\hline
\#tilltheworldends & - & false & Britney Spears & 1 \\
& & &  itunes & .75 \\
& & &  Amazon.com & .5625 \\ 
\hline
\#nowplaying & What people on Twitter & false & iTunes & .5208 \\
             & are currently listening & & Michael Jackson & .333 \\
             & to. & & Lady Gaga & .333 \\
\hline
\#nowplaying & same & true & YouTube & .8235 \\
             &  &  & Hip Hop Music & .6471 \\
             &  &  & The Notorious B.I.G. & .5883 \\
\hline
\#np         & Now playing = \#NP & false & Chris Brown\_(entertainer) & .5 \\
& & & Usher & .3125 \\
& & & Lil Wayne & .2917 \\
\hline
\#np & same & true & Chris Brown\_(entertainer) & .5 \\
& & & YouTube & .375 \\
& & & Ne-Yo & .315 \\
\hline
\#thataintwinning & -& false & Mozilla Firefox & .2291 \\
& & & Twitter & .2291 \\
& & & twitter & .1667 \\
\hline
\#thataintwinning & - & true & twitter & .5208 \\
& & & Twitter & .5 \\
& & & Two and a half men & .125 \\
\hline
\#blackpeoplemovies & - & false & Devil & .4791 \\
& & & Tyler Perry & .2708 \\
& & & Harry Potter & .2292 \\
\hline
\#blackpeoplemovies & - & true & Amazon.com & 1 \\
& & & YouTube & 1 \\
& & & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

@@

We have presented an approach for annotating Twitter hashtags with Wikipedia entities.
We have described an implementation of two variants of the method and evaluated the approach. In an evaluation we have shown that meaningful entities were found for many hashtags and that these entities remain stable over time.

However, our evaluation has shown that a direct mapping of hashtags to a single DBpedia concept is not always possible.
One reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
Another reason is the use of hashtags for different entities.
For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
The tag $\#ka$ is however also used to denote the car type Ford Ka.
Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
An approach which aims at finding relevant entities for a given search will have to be able to disambiguate homonym hashtags.
%deal with these problems.
